\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{tcolorbox}
\usepackage{xcolor}

\geometry{margin=1in}
\definecolor{ivygreen}{RGB}{0, 100, 0}
\hypersetup{
    colorlinks=true,
    linkcolor=ivygreen,
    urlcolor=ivygreen
}

\title{\vspace{-2cm}\color{ivygreen}\Huge \textbf{ACT \& SAT Calculator Program}\\ \Large \textbf{Official User Guide \& Practice Workbook}}
\author{\textbf{IvyTutoring.net}\\ Empowering students to maximize their test scores}
\date{Version 1.0}

\begin{document}

\maketitle

\tableofcontents
\newpage

\section{Introduction to the IvyTutoring Calculator Program}
Welcome to the official IvyTutoring ACT \& SAT Calculator Program for the TI-Nspire. This program has been meticulously designed to replace tedious, error-prone manual calculations with instant, perfectly-formatted, step-by-step solutions for almost every math concept tested on the ACT and SAT.

\begin{tcolorbox}[colback=ivygreen!5!white,colframe=ivygreen,title=General Tips for Navigation]
\begin{itemize}
    \item \textbf{Menu Navigation:} Press \texttt{menu} on your TI-Nspire to access the main categories (Algebra, Functions, Geometry, etc.).
    \item \textbf{Inputting Values:} Use your arrow keys or trackpad to jump between input boxes.
    \item \textbf{Instant Computation:} Solutions generate instantly as you type. You do not need to press \texttt{enter}.
    \item \textbf{Clearing Inputs:} Press the \texttt{del} button while an input box is selected to instantly clear its contents.
    \item \textbf{Scrolling:} If a result is too long to fit on the screen, select the bottom-most input box and press the down arrow to scroll through the math output.
\end{itemize}
\end{tcolorbox}

\newpage

\section{Module 1: Algebra \& Systems}
The algebra module handles everything from simple equation solving to complex $3\times3$ systems of equations, factoring, and cross-multiplication.

\subsection{Tool: Solve Equation (Single Variable)}
Solves linear and non-linear equations for a single variable.

\textbf{How to Use:} Enter the full equation (e.g., $3x+5=14$) into the input box. The program will output the exact and approximated solution.

\subsubsection*{Practice Problem}
Solve the following equation for $x$: 
\[ \frac{2x - 5}{3} = 4x + 1 \]

\subsection{Tool: 2x2 System of Equations}
Solves systems of two linear equations with two variables.

\textbf{How to Use:} Enter the first equation in Eq1 and the second equation in Eq2 exactly as they appear (e.g., $2x+3y=12$). The calculator will output the $(x, y)$ intersection.

\subsubsection*{Practice Problem}
At a movie theater, 3 adult tickets and 4 child tickets cost \$55. 2 adult tickets and 5 child tickets cost \$46. Find the cost of an adult ticket ($x$) and a child ticket ($y$):
\begin{align*}
3x + 4y &= 55 \\
2x + 5y &= 46
\end{align*}

\subsection{Tool: GCD \& LCM}
Finds the Greatest Common Divisor (Largest shared factor) and Least Common Multiple (Smallest shared multiple) of two integers.

\textbf{How to Use:} Enter two integers. The tool will break them down into prime factorizations and instantly output the GCD and LCM.

\subsubsection*{Practice Problem}
Find the greatest common factor and the lowest common multiple of 48 and 72.

\newpage
\section{Module 2: Points, Lines, \& Quadratics}
This module handles all coordinate geometry, slope calculations, and parabolic functions.

\subsection{Tool: Slope, Midpoint, \& Distance}
Given two points, this tool instantly calculates the slope ($m$), the midpoint coordinate, the exact and decimal distance between the points, and the linear equation $y=mx+b$ connecting them.

\textbf{How to Use:} Enter the coordinates $(x_1, y_1)$ and $(x_2, y_2)$. The program provides step-by-step calculations for every metric.

\subsubsection*{Practice Problem}
A line segment connects the points $A(-3, 4)$ and $B(5, -2)$. Find the length of the segment, its midpoint, and the equation of the line passing through it.

\subsection{Tool: Quadratic Formula \& Vertex}
Analyzes quadratic functions in standard form ($ax^2 + bx + c$). Assesses the discriminant, finds exact real and complex roots, and calculates the vertex $(h, k)$.

\textbf{How to Use:} Enter the coefficients $a$, $b$, and $c$. The output will walk you step-by-step through the discriminant formula $b^2-4ac$ and provide both fractional and decimal solutions.

\subsubsection*{Practice Problem}
Find the roots and the coordinates of the vertex for the parabola given by:
\[ f(x) = 2x^2 - 12x + 22 \]


\newpage
\section{Module 3: Functions}
The functions module allows you to evaluate, compose, and find the intersection of custom mathematical functions.

\subsection{Tool: Intersections ($f(x) = g(x)$)}
Finds where two functions intersect on the Cartesian plane.

\textbf{How to Use:} Enter $f(x)$ and $g(x)$. The tool sets them equal to one another, solves for $x$, plugs $x$ back in to find $y$, and yields exact coordinate points.

\subsubsection*{Practice Problem}
Find the coordinates where the line $g(x) = 2x + 5$ intersects the parabola $f(x) = x^2 - 3$.

\subsection{Tool: Function Composition ($f(g(x))$)}
Evaluates composite functions.

\textbf{How to Use:} Provide the expression for $f(x)$, the expression for $g(x)$, and the value $x$ to evaluate at. 

\subsubsection*{Practice Problem}
If $f(x) = x^2 + 1$ and $g(x) = 3x - 2$, find the value of $f(g(4))$.

\newpage
\section{Module 4: Sequences \& Probability}
This module simplifies repetitive sequence calculations and handles permutations and combinations.

\subsection{Tool: Arithmetic \& Geometric Sequences}
Calculates terms and series sums for arithmetic (additive) and geometric (multiplicative) sequences.

\textbf{How to Use:} For geometric, enter the first term $a_1$, the common ratio $r$, and the term number $n$. The tool will evaluate the $n$th term, the sum of the first $n$ terms, and the sum to infinity if it converges.

\subsubsection*{Practice Problem}
A bouncing ball is dropped from a height of 100 feet. Each time it bounces, it reaches 75\% of its previous height. What is the height of the ball after the 5th bounce, and what is the total vertical distance the ball will travel before coming to rest?

\subsection{Tool: Permutations \& Combinations}
Calculates $nPr$ (where order matters, e.g., passwords or seating) and $nCr$ (where order does not matter, e.g., picking a committee).

\textbf{How to Use:} Enter the total number of items ($n$) and the number chosen ($r$). 

\subsubsection*{Practice Problem}
A student club has 12 members. 
\begin{enumerate}
    \item How many ways can they elect a President, Vice President, and Secretary? 
    \item How many ways can they choose a 3-person delegation to attend a conference?
\end{enumerate}

\newpage
\section{Module 5: Matrices}
Perform matrix operations securely and without writing out arrays by hand.

\subsection{Tool: Matrix Multiplication ($A\times B$)}
Multiplies two matrices.

\textbf{How to Use:} Input the matrices using bracket formats with semicolons separating rows (e.g., \texttt{[1,2;3,4]}). 

\subsubsection*{Practice Problem}
Evaluate the product of $A$ and $B$:
\[ A = \begin{bmatrix} 2 & -1 \\ 3 & 4 \end{bmatrix}, \quad B = \begin{bmatrix} 5 & 0 \\ -2 & 1 \end{bmatrix} \]

\vspace{2cm}
\begin{center}
\textbf{Need more help with your TI-Nspire or test prep in general?} \\
Visit \url{https://IvyTutoring.net} to schedule a session with an expert tutor today!
\end{center}

\end{document}
